Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/experiments.tex

\paragraph{Quantitative experiments}
We benchmark DAU against DDPG on classic control benchmarks: Pendulum, Cartpole, BipedalWalker, Ant and Half-Cheetah environments from OpenAI Gym. For Pendulum and Ant, DDPG is able to learn for the highest $\deltat$ but fails for the others, while DAU remains reasonably invariant to the time discretization. On Bipedal Walker, DDPG is never able to learn while DAU is achieving decent performance for all the $\deltat$'s. On Cartpole and Half Cheetah, results are less clear. On Cartpole, noise dominates, which makes interpretation difficult. On Half Cheetah, DAU is not clearly more invariant to time discretization than DDPG. This could be explained by the multiple suboptimal regimes that coexist in the half cheetah environment (walking on the head, walking on the back), and that DAU may fail to correctly weight the performance of each regime (as explained in Section \ref{sec:discussions}).

>>>>

\paragraph{Quantitative experiments.}
We benchmark DAU against DDPG on classic control benchmarks: Pendulum,
Cartpole, BipedalWalker, Ant, and Half-Cheetah environments from OpenAI
Gym. For Pendulum and Ant, DDPG is able to learn for the highest
$\deltat$ but fails for the others, while DAU remains reasonably
invariant to the time discretization. On BipedalWalker, DDPG is never
able to learn while DAU is achieving decent performance for all the
$\deltat$'s. On Cartpole and Half-Cheetah, the results are less clear. On
Cartpole, noise dominates, which makes interpretation difficult. On Half
Cheetah, DAU is not clearly more invariant to time discretization than
DDPG. This could be explained by the multiple suboptimal regimes that
coexist in the half cheetah environment (walking on the head, walking on
the back), and that DAU may fail to correctly weight the performance of
each regime (as explained in Section \ref{sec:discussions}).
